From physical principles to ???

### 2016-01-25 2015CompleteDerivation/completeDerivation.tex
Minor changes for decomposable systems

Consider the following expression:
\begin{align*}
\mathcal{c} = \sum\limits_{i \in \mathbbm{I}} a_i \mathcal{e}(i)
\end{align*}
$\mathbbm{I}$ represents all the possible values of a state variable representing the best description of an infinitesimal part that a composite system can give. $\mathcal{e}(i)$ represents a composite system made of a unit amount of particles, all prepared in the state determined by $i$. $a_i$ represents a transformation that changes the whole state, without affecting the value $i$ for any infinitesimal part. For a classical system, $i$ represents the full information about the infinitesimal part, and therefore includes the value of all state variables; the only transformation left is increasing/decreasing the amount of particles by a scalar multiple. For a different system, where $i$ does not represent the full state of the parts, $\mathcal{e}(i)$ will be an ensemble and $a_i$ also represents an internal transformation of such ensable. This is intuitively how we decouple the composite state into the part $i$ that describes the infinitesimal parts, and the part $a_i$ that describes how the parts are composed. Giving a full description of the state space of a decomposable system means fully characterizing these components: the state variable $\mathbbm{I}$ and the set of transformations $A$. In the classical case $\mathcal{e}(i)$ form a basis of a real vector space, where $i$ is the set of state variable to identify the state of an an infinitesimal part, and $a_i$ a real valued coefficient that represents the amount of particles in each state, which describes how the parts are combined.

@@

We now claim that the state space $\mathcal{C}$ is a vector space over $\mathbbm{R}$. The abelian group $\mathcal{C}$ can be extended with the operations defined by $A$, as each element $a \in A$ is a map $a : \mathcal{C} \rightarrow \mathcal{C}$. The map has the following properties: $(a_1 + a_2) \mathcal{c} = a_1 \mathcal{c} + a_2 \mathcal{c}$, increasing the size of the system by the sum of two constant is the same as combining the separate increases, and $a (\mathcal{c}_1 + \mathcal{c}_2) = a \mathcal{c}_1 + a \mathcal{c}_2$, increasing the size of the total system is the same as the combination of the increased parts. $\mathcal{C}$ is a vector space over $A$, which is a field and isomorphic to $\mathbbm{R}$.

>>>>

Consider the following expression:
\begin{align*}
\mathcal{c} = \sum\limits_{i \in \mathbbm{I}} a_i \mathcal{e}(i)
\end{align*}
$\mathbbm{I}$ represents all the possible values of a state variable representing the best description of an infinitesimal part that a composite system can give. $\mathcal{e}(i)$ represents a composite system made of a unit amount of particles, all prepared in the state determined by $i$. $a_i$ represents a transformation that changes the whole state, without affecting the value $i$ for any infinitesimal part. For a classical system, $i$ represents the full information about the infinitesimal part, and therefore includes the value of all state variables (i.e. the state vector); the only transformation left is increasing/decreasing the amount of particles by a scalar multiple. For a different system, where $i$ does not represent the full state of the parts, $\mathcal{e}(i)$ will be an ensemble and $a_i$ also represents an internal transformation of such ensemble. This is intuitively how we decouple the composite state into the part $i$ that describes the infinitesimal parts, and the part $a_i$ that describes how the parts are composed. Giving a full description of the state space of a decomposable system means fully characterizing these components: the state variable $\mathbbm{I}$ and the set of transformations $A$. In the classical case $\mathcal{e}(i)$ form a basis of a real vector space, where $i$ is the state vector for an infinitesimal part, and $a_i$ a real valued coefficient that represents the amount of particles in each state, which describes how the parts are combined.

@@

We now claim that the state space $\mathcal{C}$ is a vector space over $\mathbbm{R}$. The abelian group $\mathcal{C}$ can be extended with the operations defined by $A$, as each element $a \in A$ is a map $a : \mathcal{C} \rightarrow \mathcal{C}$. The map has the following properties: $(a_1 + a_2) \mathcal{c} = a_1 \mathcal{c} + a_2 \mathcal{c}$, increasing the size of the system by the sum of two constant is the same as combining the separate increases, and $a (\mathcal{c}_1 + \mathcal{c}_2) = a \mathcal{c}_1 + a \mathcal{c}_2$, increasing the size of the total system is the same as the combination of the increased parts. $\mathcal{C}$ is a module over $A$, which is a field and isomorphic to $\mathbbm{R}$.
